A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-28 paper/paper.tex
Add a paragraph to the semantic typing section

\section{Semantic Typing and Consistency}
\label{sec:logrelproof}

>>>>

\section{Semantic Typing and Consistency}
\label{sec:logrelproof}
The logical relation we define in Figure~\ref{fig:logrel} does not
include cases for variables. Likewise, for the base types such as
boolean and equality, the output set $[[S]]$ contains only terms that
evaluate to closed terms. To generalize our logical relation to open
terms, we define the semantic typing judgment by closing the open
terms with a substitution whose codomain consists of terms that
respect the interpretation of the types from the context. The full
definition of semantic typing ($[[ G |= a : A]]$) is presented in
Figure~\ref{fig:semtyping}.
